TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-11 paper/paper.tex
Added CUBIC algorithm

		The CUBIC algorithm

>>>>

		The CUBIC algorithm is a successor of the BIC algorithm \cite{cubic-tcp-congestion}. In case of a loss event $W_{max}$, which is the maximum window size, is registered. This is followed by a multiplicative decrease of the congestion window by factor $\beta$. If an ACK in congestion avoidance is received and the current window size $cwnd$ is less than $W_{max}$, the algorithm uses the concave profile to increase the window size according to the formula: $cwnd = \frac{W(t+RTT)-cwnd}{cwnd}$. If $cwnd$ is larger than $W_{max}$, the convex profile is used to increase the window size according to the same formula as the concave profile. In both formulas $t$ is the time elapsed from the last window reducation.
